%-------------------------
% Resume in Latex
% Author : Cameron Brill
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\usepackage{tgadventor}
%\renewcommand*\familydefault{\sfdefault}
%\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont[
  Ligatures=TeX,
  UprightFont=*-Light,
  ItalicFont=*-LightItalic,
  BoldFont=*-SemiBold
]{Poppins}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemDescription}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeHonorsItem}[1]{
  \item\small{
    #1 \vspace{-6pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectItem}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small Skills Used: #2} \\
    \end{tabular*}\vspace{-5pt}
  } 

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeProjectListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeProjectListEnd}{\end{itemize}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeInnerItemListStart}{\begin{itemize}}
\newcommand{\resumeInnerItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://cameronbrill.me/}{\Large Cameron Brill}} & \href{mailto:contact@cameronbrill.me}{contact@cameronbrill.me}\\
  \href{http://cameronbrill.me/}{cameronbrill.me} & 469-401-1162 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Science in Computer Science;  GPA: 3.41}{Expected Dec 2021}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \end{tabular*}\vspace{-5pt}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Microsoft}{Redmond, Washington}
      {Software Engineer Intern}{May 2020 - Present(Ending Aug 2020)}
      \resumeItemListStart
        \resumeItemDescription{Developing novel streaming telemetry PoC with \textbf{gRPC, Telegraf, InfluxDB, and Grafana}.}
        \resumeItemDescription{Planning production deployment accross \textbf{4000} network switches with \textbf{Ansible} automation.}
        \resumeItemDescription{Constantly interfacing with vendors and external orgs to properly and efficiently execute project.}
      \resumeItemListEnd

    \resumeSubheading
      {State Farm}{Dallas, TX}
      {Software Engineer Intern}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItemDescription{Spearheaded microservice development in \textbf{Java Spring Boot} for web app used by 60k insurance agents daily.}
        \resumeItemDescription{Increased overall code throughput by \textbf{18\%} with custom \textbf{GitLab CI/CD} pipelines and cloud-enabled Config Server.}
        \resumeItemDescription{Created unit tests (JUnit) and UI tests to improve testing coverage to \textbf{99\%} for above mentioned project.}
      \resumeItemListEnd

    \resumeSubheading
      {Dynamic MC}{College Station, TX}
      {Founder and Software Engineer}{Nov 2019 - Present}
      \resumeItemListStart
        \resumeItemDescription{Open-source solution to affordable Minecraft servers. Uses \textbf{AWS EC2} hourly instances for efficient spending.}
        \resumeItemDescription{Currently developing AWS connection API in \textbf{Go} and overseeing a developer creating frontend in React.}
      \resumeItemListEnd
      
    \resumeSubheading
      {TAMUhack}{College Station, TX}
      {Tech Lead}{Oct 2019 - Present}
      \resumeItemListStart
        \resumeItemDescription{Led team of 5 developers to maintain and generalize \textbf{Django} registration system used by \textbf{4000+} people.}
        \resumeItemDescription{Secured \textbf{\$4k} in sponsorship contributing to overall \$75k of funding for the event.}
      \resumeItemListEnd

    \resumeSubheading
      {Reveal Modern}{Dallas, TX}
      {Software Engineer Intern and Full-Stack Developer}{Spring 2018 and Spring 2019 Respectively}
      \resumeItemListStart
        \resumeItem{2019}
          {Automated processes with \textbf{Python} and ads with \textbf{JavaScript} reducing developer workload by \textbf{25\%}.}
        \resumeItem{2018}
          {Developed webpages for 10+ clients using HTML/CSS, \textbf{Javascript}, and PHP/WordPress.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects} 
  \resumeProjectListStart 
    \resumeProjectItem{True Colors}{Python, Pandas, Requests, Beatiful Soup, Jupyter, MongoDB Atlas}
      \resumeItemListStart
        \resumeItemDescription{Web scraper that analyzes a company's reaction to and contribution to society during a pandemic.}
        \resumeItemDescription{Scraped data with Requests, cleaned with Pandas and Beautiful Soup, and hosted on MongoDB Atlas cluster.}
      \resumeItemListEnd
    \resumeProjectItem{InFlightful}{Python, Pandas, \LaTeX}
      \resumeItemListStart
        \resumeItemDescription{Application and analysis for data science competition between undergraduates and graduates at A\&M.}
        \resumeItemDescription{Created models to analyze common factors in causing flight delays and predict flight delays.}
      \resumeItemListEnd
    \resumeProjectItem{The Sustainability Index}{Javascript, Express.js, MongoDB, Python, Pandas}
      \resumeItemListStart
        \resumeItemDescription{Stock index coupled with scores for environmental+social impact and labor practices.}
        \resumeItemDescription{Created API with Express.js and MongoDB and used Pandas to clean and join 4 company info datasets.}
      \resumeItemListEnd
    \resumeProjectItem{Taco 'bout It}{Python, Flask, Pandas}
      \resumeItemListStart
        \resumeItemDescription{Website to tell potential taco/burrito shop owners competitive location and pricing strategies.}
        \resumeItemDescription{Created API with Flask and cleaned and analyzed taco/burrito restaurant data with Pandas.}
      \resumeItemListEnd
  \resumeProjectListEnd

%--------Honors and Awards------------ 
\section{Honors \& Awards}
  \resumeSubHeadingListStart 
    \resumeSubItem{MLH Top 50 Hacker of 2020}{Based on my projects and community impact, out of 100,000 students who participated in hackathons, Major Leauge Hacking chose my story to be one of 50 recognized on this list.}
    %--won \%5800 in awards at 12+ hackathons
    \resumeSubItem{1517 Fellow}{Selected from 99 teams to be awarded \$11k in funding at hack:now to create a startup.}
    \resumeSubItem{Competitions I've Won At}{HackTX19, HackSMU19, HackUNT19/20, 
    Wacode19, HackHouston19, RowdyHacks20, Hack Kosice Digital20, Hack Quarantine20, TAMIDS Data Science 
    Competition 2020, HackDSC20, hack:now20, CitrusHacks20, EarthXHack20.}
    \resumeSubItem{Hackathons I've Mentored At}{Howdy Hack 2019(Top Mentor), TAMUhack 2020(Organizer), Hacklahoma 2020.} 
  \resumeSubHeadingListEnd
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: (Profficient): Python, Java, Typescript, Javascript, (Familiar): GoLang, C++, SQL}
      \hfill
    }\vspace{-5pt}
    \item{
      \textbf{Technologies}{: AWS, Tensorflow, Keras, Pandas, Flask, NodeJS, Express, Spring Boot}
      \hfill
    }\vspace{-6pt}
    \item{
      \textbf{Databases/Environments}{: PostgreSQL, MySQL, MongoDB, UNIX (Arch Linux, Debian Linux, MacOS)}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
